Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-22 docs/report/report.tex
stans updates

In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variaty of angles. Overall none of these approach have completely solved the problem and most approaches only work on very slow moving platforms with little or no wind disturbances.

@@

\subsection{Measurement and State Estimation using AprilTags}
One of the challenges we faced when estimating the quadrotor state using AprilTags was the computational resource required to sustain a rate of atleast 20hz. This problem is exacerbated when the image size increases, as do the computational time needed to extract the pose estimate of the AprilTag, from our initial experimentation the computational time grows exponentially as image size increases as shown in (add a figure here). This problem was also noted in the work of \cite{Ling2014} where he addressed the issue by reducing the brightness of the image so that the majority of the image is black except for the AprilTag, thus reducing image processing requirements. An example of this implementation is shown in Figure~\ref{fig:ling_apriltags} This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also the lost of robustness in estimating the AprilTags.

@@

\subsubsection{AprilTag Inception}
To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending). This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag. Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture. An example of this procedure is highlighted in Figure \ref{fig:apriltagInception}.

@@

\subsection{Controller and State Monitoring}
In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times. The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just abvove ($\approx 1m$) the landing target inorder to minimize time and energy requirements of the landing maneouver.

@@

\section{Experimental Hardware}
The quadrotor used in this experiment assembled from a DJI F450 quadrotor frame, 4 Emax 2213-935KV motors with complementary DJI E310 420S 20A electronic speed controllers. The flight controller selected for the project was a Pixhawk v2.4 running the PX4 firmware stack. An Odroid XU4 was selected as the onboard computer to processes captured images from a video stream and sends attitude commands via usb to the Pixhawk based of the PID controllers and current state as outlined above. Communication between the Odroid and the Pixhawk is handled by the mavros package which is a wrapper around the popular Mavlink communication protocal for UAVs.  Video was captured using a PointGrey Firefly 2.0 camera operating 60 frames per second (fps) with a resolution of 640 by 480 pixels along with a FujiFilm 135 degree FOV lens. The quadrotor and camera are highlighted in Figure \ref{Quadrotor}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
	\caption{DJI F450 with Pixhawk v1.5}
	\label{Quadrotor}
\end{figure}

\section{Results}
\begin{itemize}
	\item Results of the image stuff
	\begin{itemize}
		\item Plot of FPS vs distance
		\item Plot of true state vs mocap state?
	\end{itemize}

	\item PID/Control results 
	\begin{itemize}
		\item Plot XY for the controller loop
		\item Optimal PID settings
		\item How we got there
		\item Decent plot (V as a function of Z)
		\item Video?
	\end{itemize}

\end{itemize}

\subsection{AprilTag Results}
\begin{figure}
	\centering
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
		\caption{}
		\label{fig:pid_roll}
	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
		\caption{}
		\label{fig:pid_roll}
	\end{subfigure}
\end{figure}

\subsection{PID and Controller Results}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Pitch_x_true_and_obs.eps}
	\caption{Position Controller - Pitch Command}
	\label{fig:pid_roll}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Pitch_Controls.eps}
	\caption{Position Controller - Pitch Control Signal Components}
	\label{fig:pid_roll}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Roll_y_true_and_obs.eps}
	\caption{Position Controller - Roll Command}
	\label{fig:pid_roll}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Roll_Controls.eps}
	\caption{Position Controller - Roll Control Signal Components}
	\label{fig:pid_roll}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Elevation_True_and_obs.eps}
	\caption{Position Controller - Thrust Command}
	\label{fig:pid_roll}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Elevation_Controls.eps}
	\caption{Position Controller - Thrust Signal Components}
	\label{fig:pid_roll}
\end{figure*}

So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.

\section{Conclusion and Future Work}

\section{Proposed Future Work}
In the coming weeks, the PID controllers tested and developed using the MOCAP system will be tested using state estimates that are produced from the AprilTag library and the image preprocessing methods outlined in section \textbf{\textit{OUTLINE OF IMAGE PREPROCESSSING}}.

One major issue highlighted in Ling \cite{Ling2014} is that due to the relatively long processing time of the AprilTags library, the estimated state obtained at a time $t$ does not actually represent the current state due to a time lag. This time lag as outlined in \cite{Ling2014} and defined in \ref{Detection Delay} must be accounted for when using the camera to estimate state. Currently our proposed method to measure this lag is to use the MOCAP system to provide a ground truth for the state from which we can estimate the estimated state.

\begin{equation}
\label{Detection Delay}
    t_{\text{capture}} = t - \delta t_{\text{camera}} + \delta t_{\text{detection}}
\end{equation}

The next issue that will need to be address is the problem of the camera view. The dynamics of a quadrotor work in such a way that in order to move towards a goal point, the quadrotor must tilt away from the target which leads to problems with maintaining a view of the target when desired roll or pitch angles are greater than approximately 10 degress. This issue can either be addressed by mounting the camera at an angle or by adding a gimbals to the the quadrotor such that the gimbal will be sent commands by the onboard computer that will maintain a constant view of the target regardless of the commanded roll and pitch.

Both of the above solutions have significant implementation questions that will have to be answered. If using the fixed camera angle, then the yaw of the qaudrotor will need to be controlled by a PID controller, similar to the the PID controllers to the roll and pitch. In the case of significant wind, the quadrotor will need to rotate itself such that the front of the quad is pointed into the wind during the final decent.

If a gimbal is used there are two issues that arise. First a new set of controllers that send roll, pitch and yaw commands to the gimbal such that the camera it is attached to maintains a centred view of the target platform must be developed. These controllers will likely be similar to the PID controllers developed above and so they are not considered to be terrible difficult to define are implement. The more difficult part of using a gimbal is related to resuming the gimbal state, which in cheaper gimbals do provide. All of the gimbals that have been researched as part of this project do not provide state feedback and so they are considered to be open loop. Therefore in order to use such a gimbal the user will need to assume the commanded gimbal position is equal to the true gimbal position, from which a transform between the quad rotor and the gimbal can be made.

\bibliography{report}{}
\bibliographystyle{ieeetr}

\end{document}

>>>>

In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variety of angles. Overall none of these approach have completely solved the problem and most approaches only work on very slow moving platforms with little or no wind disturbances.

@@

\subsection{Measurement and State Estimation using AprilTags}
\label{subsec:AprilTag}
One of the challenges we faced when estimating the quadrotor state using AprilTags was the computational resource required to sustain a rate of atleast 20hz. This problem is exacerbated when the image size increases, as do the computational time needed to extract the pose estimate of the AprilTag, from our initial experimentation the computational time grows exponentially as image size increases as shown in (add a figure here). This problem was also noted in the work of \cite{Ling2014} where he addressed the issue by reducing the brightness of the image so that the majority of the image is black except for the AprilTag, thus reducing image processing requirements. An example of this implementation is shown in Figure~\ref{fig:ling_apriltags} This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also the lost of robustness in estimating the AprilTags.

@@

\subsubsection{AprilTag Inception}
To address both the decreasing state update rate as a function of proximity and reduce the probability of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending). This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag. Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture. An example of this procedure is highlighted in Figure \ref{fig:apriltagInception}.

@@

\subsection{Controller and State Monitoring}
\label{subsec:position_controller}
In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times. The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just above ($\approx 1m$) the landing target to minimize time and energy requirements of the landing manoeuvre.

@@

\section{Results}
The methods outlined in sections \ref{subsec:AprilTag} and \ref{subsec:position_controller} were implemented and tested on real quadrotor with an onboard computer and camera. The quadrotor is assembled from a DJI F450 quadrotor frame, 4 Emax 2213-935KV motors with complementary DJI E310 420S 20A electronic speed controllers. A Pixhawk v2.4 running the PX4 firmware stack was selected for the flight controller and an Odroid XU4 was used as an on-board computer to processes process video captured from a using a PointGrey Firefly 2.0 camera operating 60 frames per second (fps) with a resolution of 640 by 480 pixels through a FuijiFilm 135 degree FOV lens. The camera calibration was done using the ROS camera calibration package.

Images captured from the video stream are then processed using the AprilTag library after passing through the preprocessing steps outlined in \ref{subsec:AprilTag} and the estimated state is used by the PID controller (outlined in \ref{subsec:position_controller} and also running on the Odroid) to produce attitude commands that cause the quadrotor to move towards a goal location. All attitude commands are send to the Pixhawk from the Odroid via usb and rely heavily on the Mavros package, which is a wrapper around the popular Mavlink communication protocol.

Using this testbed both the accuracy of the AprilTag state estimation was evaluated in the following sections. At this point in time a motion capture system was used in place of the AprilTag library to provide state estimates as it was found to be more reliable for initial testing purposes. In the coming week the PID controllers will also be tested using only the state estimates from the AprilTag library.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
	\caption{DJI F450 with Pixhawk v2.4}
	\label{Quadrotor}
\end{figure}

\subsection{Evaluation of AprilTag Accuracy and Update Rate}
To evaluate the accuracy of the AprilTag and effects that the adaptive windowing procedures have on the state estimations an Optitrack motion capture system (MOCAP) was used to provide a ground truth. By monitoring the pose of both the camera and the AprilTag in the MOCAP system, the series of measurements were taken using the MOCAP system to calculate the pose of the AprilTag relative to the camera from a variety of ranges and angles. A comparison between the estimated pose from the AprilTag and the MOCAP system as a function of distance is highlighted in Figure \ref{fig:AprilTag_eval}. Figure \ref{fig:AprilTag_eval} also highlights the rate at which state estimates are received from the AprilTag library after being passed through the adaptive windowing procedure. A demo of the AprilTag pose estimation can also be seen in this 
\href{https://www.youtube.com/watch?v=BBMlQphrqCY&index=19&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{video}.

\begin{figure}	
	\centering
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
		\caption{}

	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
		\caption{}

	\end{subfigure}
	\caption{Evaluation of AprilTag state estimation and update rate as functions of distance}
	\label{fig:AprilTag_eval}	
\end{figure}

From Figure \ref{fig:AprilTag_eval} it appears that the average error of the estimated euclidean distance compared to MOCAP ground truth is within approximately $\pm 20 cm$ for any measurements between 0 and 3 meters. Due to the limited range of the MOCAP system distances greater than 3 m between the camera and the AprilTag were not tested. The system was also able to maintain a frame rate of approximately 30 fps in cases camera is less then 2 meters away from the AprilTag while producing estimates with an error within approximately $\pm 0.05 cm$. In future, an analysis of the sources of error in Figure \ref{fig:AprilTag_eval} will be conducted as well as evaluation of the error as a function of angle between the AprilTag and the camera.

It is suspected that the PointGrey Camera used in this test was not operating at the requested frame rate of 60 fps. This was not noted until after analysising the data and will be investigated this coming week. In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resting the frame rate from 30 fps to 60 fps with no warning or indication. If this is the case, then the update rate of the AprilTag library on the Odroid may actually be faster than what is shown in Figure \ref{fig:AprilTag_eval}. In cases where a more powerful computer can be used, the adaptive image processing method results in the AprilTag library operating at 60 fps with no delay, making it extremely useful on machines that can leverage greater computational power.

\subsection{PID and Controller Results}
The PID controllers dervied in section \ref{subsec:position_controller} were tested on the quadrotor using the MOCAP system. Due to time constraints evaluation of the PID controller was only conducted using the MOCAP system to provide state estimates, but in the coming week further tests using the AprilTag system will be conducted. After a signifcant amount of testing the following values for the proportional, derivitave and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers. Using state information from the MOCAP system, the yaw of the quadrotor was fixed at zero degrees for all of the following tests.

\begin{center}
	\vspace{-0.4cm}
	\begin{tabular}{l r}
		\hline
		\textbf{Roll Controller} \\
		\hline
		$K_{p}$ &  0.205 \\
		$K_{i}$ & 0.05 \\
		$K_{d}$ &  0.02 \\
		\\
		\hline
		\textbf{Pitch Controller} \\
		\hline
		$K_{p}$ & 0.205 \\
		$K_{i}$ & 0.05 \\
		$K_{d}$ & 0.02 \\
		\\
		\hline
		\textbf{Thrust Controller} \\
		\hline
		$K_{p}$ & 0.2 \\
		$K_{i}$ & 0.0 \\
		$K_{d}$ & 0.02 \\
	\end{tabular}
\end{center}

Figures \ref{fig:pid_roll_command} \ref{fig:pid_roll_error},	\ref{fig:pid_pitch_command}, \ref{fig:pid_pitch_error}, \ref{fig:pid_thrust_command}, \ref{fig:pid_thrust_error} higlight the PID position control signal (roll, pitch and thrust) and corresponding proportional, integral and derivative error components while a quadrotor was set to hover at $(0, 0, 1)$ for approximately 65 seconds. Large disturbances were applied manually to the hovering quadrotor with a testing apparatus (a plank of wood) to test the correction behaviour of the position controller implemented. These disturbances are applied at the 15, 21, 37, and 57 second marks in all six Figures. In the case of the elevation controller, there was no integral term used due to the risk of a suck throttle occurring in cases where the quadrotor did not detect landing and tack off correctly.

From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} that the roll and pitch commands are bounded to $\pm 20^o$ further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds. Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time. A video of the plotted dataset can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.

In all cases there is a significant amount of noise on the derivative error term as highlighted in Figures \ref{fig:pid_roll_error}, \ref{fig:pid_pitch_error}, and \ref{fig:pid_thrust_error}. It is suspected that this large error is due to the small time step of 0.01 seconds used in the calculation of the derivative term which has side effect of greatly amplifying any noise in the MOCAP state estimations. In cases where the MOCAP measurement did not correctly correspond to the current true state of the vehicle large spikes can be noted which appears around the 9 second mark in Figures \ref{fig:pid_roll_error}, \ref{fig:pid_pitch_error}, and \ref{fig:pid_thrust_error}. The noise in the MOCAP system can be reduced by adding additional markers to the quad and by making a more rigid frame to mount the tracking markers.

These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered far to aggressive for the quadrotor used in these experiments. Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees. Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag. Such a test will be the focus of the majority of effort in the coming weeks.

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Pitch_x_true_and_obs.eps}
	\caption{Position Controller - Pitch Command}
	\label{fig:pid_roll_command}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Pitch_Controls.eps}
	\caption{Position Controller - Pitch Control Signal Components}
	\label{fig:pid_roll_error}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Roll_y_true_and_obs.eps}
	\caption{Position Controller - Roll Command}
	\label{fig:pid_pitch_command}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Roll_Controls.eps}
	\caption{Position Controller - Roll Control Signal Components}
	\label{fig:pid_pitch_error}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Elevation_True_and_obs.eps}
	\caption{Position Controller - Thrust Command}
	\label{fig:pid_thrust_command}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Elevation_Controls.eps}
	\caption{Position Controller - Thrust Signal Components}
	\label{fig:pid_thrust_error}
\end{figure*}

\section{Conclusions and Future Work}
A set of algorithms were developed to provide fast, reliable and accurate estimations of state between a landing pad and a quadrotor using a series of image preprocessing methods and the MIT AprilTags library. These methods were tested and evaluated using a motion capture system to provide ground truth and were shown to provide update rates of greater than 20 Hz for a low power onboard, quadrotor mounted computer system. A set of PID controllers were developed, tested and evaluated using the same motion capture system to provide state estimates and a ground truth. A set of stable yet responsive PID gains were found and tested using this system and an evaluation of their behaviour in the presence of large disturbances was conducted.

In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure. Once such a landing can be performed consistently in the face of minor disturbances it, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.

\bibliography{report}{}
\bibliographystyle{ieeetr}
\end{document}
